Data Appendix to \"The impact of weather events on schooling outcomes\

### 2020-04-14 data_appendix_all_years.Rmd
got the final data set

```{r combine household datasets}
all_years <- hh_2005 %>% 
  #bind_rows(hh_2005, hh_2006, hh_2007, hh_2011, hh_2012)
  rbind(hh_2005, hh_2006)

@@

children <- subset(total_data, age < 18 & age > 4, select = c("hh_id", "age", "sex", "literacy", "dept", "urb_rur", "income", "assist", "reason", "register", "school_level", "grade", "repeated", "floods", "droughts"))

>>>>

```{r combine household datasets}
all_years <- hh_2005 %>% 
  rbind(hh_2005, hh_2006, hh_2007, hh_2011, hh_2012)
  #bind_rows(hh_2005, hh_2006, hh_2007, hh_2011, hh_2012)
  #rbind(hh_2005, hh_2006)

@@

children <- subset(total_data, age < 18 & age > 4, select = c("hh_id", "age", "sex", "relation", "literacy", "dept", "urb_rur", "income", "assist", "reason", "register", "school_level", "grade", "repeated", "floods", "droughts", "year"))

```{r combining household head characteristics with children dataset}
hh_head_2 <- hh_head %>%
  select(sex, age, literacy, hh_id) %>%
  rename (female_parent = sex,
          parent_age = age,
          parent_literacy = literacy)

total_children <- children %>%
  left_join(hh_head_2)

```
```{r creating summary statistics}

export_summary_table(dfSummary(total_children))
